---
title: "p8105_hw1_yl4362"
author: "Yiting Li"
date: "9/17/2020"
output: github_document
---

This is the hw1 of yl4362! 

```{r}
library(tidyverse)
```

# Problem 1

## Data frame
**The code chunk below creates a data frame for problem 1.**
```{r}
prob1_df = tibble(
  samp = rnorm(10, mean = 0, sd=1),
  samp_gt_0 = samp > 0,
  char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "j", "i"),
  factor_vec = factor(c("low", "low", "high", "high", "middle", "middle", "low", "high", "middle", "high"))
)
```

**Take the mean of each variables**
```{r}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```
It works for numeric and logical vector because logical vector will be automatically regarded as numeric (0,1). But it does not work for character and factor.

**Apply `as.numeric` to variables**
```{r, eval = FALSE}
as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```
After applying `as.numeric`, results of 'samp', 'samp_gt_0', and 'factor_vec' were successfully converted to numeric values because factor vector is used to refer to a qualitative relationship.  But it does not work for character vector because they are combinations of letters.

It partly explains the results of take the mean attempt, becasue it shows 'samp' can 'samp_gt_0' can be converted to numeric values.

## Convert the logical vector
**Convert the logical vector to other data types and calculate them**
```{r}
as.numeric(pull(prob1_df, samp_gt_0))*pull(prob1_df, samp)
as.factor(pull(prob1_df, samp_gt_0))*pull(prob1_df, samp)
as.numeric(as.factor(pull(prob1_df, samp_gt_0)))*pull(prob1_df, samp)
```


# Problem 2

## Descriptions of the `penguins` dataset
```{r}
data("penguins", package = "palmerpenguins")
```
The names / values of important variables in the `penguins` dataset are shown below:
```{r} 
str(penguins)
```

The size of the dataset is `r nrow(penguins)` and `r ncol(penguins)`.

The mean flipper length is `r mean(pull(penguins, flipper_length_mm), na.rm = TRUE)`mm.

## Create a scatterplot
```{r}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
ggsave("scatter_plot.pdf", height = 4, width = 6)
```